# Overrepresentation analysis
```{r, include=FALSE}
load('cache.RData')
library(RColorBrewer)
library(Seurat)
library(patchwork)
library(ggplot2)
library(dplyr)
library(hdf5r)
library(stringr)
library(biomaRt)
library(kableExtra)
library(knitr)
library(pdftools)
library(viridis)
library(openxlsx)
library(SeuratDisk)
library(SeuratData)
library(ComplexHeatmap)
library(plotly)
library(iDEA)
library(fgsea)
library(clusterpval)
library(msigdbr)
library('pbmc3k.SeuratData')
library('cbmc.SeuratData')
library('ifnb.SeuratData')
library('panc8.SeuratData')
data("pbmc3k")
data("cbmc")
data("ifnb")
data("panc8")
```
Overrepresentation analysis (ORA) actually has quite a simple formula to compute the p-value for a given gene set. If N is the total number of genes in the background distribution (the list of all genes across all the gene sets), M the number of genes within the gene set that are in the background, n the size of the list of DE gnes, and k the number of DE genes that are in the gene set, then the p-value can be computed with the hypergeometric distribution

$$ p = 1 - \sum_{i=0}^{k-1} \frac{\binom{M}{i} \binom{N-M}{n-i}}{\binom{N}{n}} $$
p-values should then be adjusted for multiple comparison.

We will use the package `clusterProfiler` to do this computation as well as adjust. Since in ORA we only want the list of DE genes, we filter out `ctl_vs_stim` to only keep genes with pvalue < 0.05. With this list and the `filtered_genes` dataframe from `misgdbr` we have enough inputs for the `clusterProfiler::enricher` function to do our analysis.

```{r}
library(clusterProfiler)
de_genes <- filter(ctl_vs_stim, p_val_adj < 0.05) %>% rownames()
ora <- enricher(gene=de_genes, pvalueCutoff = 0.05, pAdjustMethod="BH",
         TERM2GENE=filtered_genes)
ora@result
```

As we can see, the interferon signaling pathway has a significant pvalue, but the other 3 pathways do not. The results also include a GeneRatio and a BgRatio, corresponding to M/N and k/n respectively. This is in line with our expectations. Although ORA is rather simple, it's a good first step to check your expectations quickly before moving on to more complicated analyses.


```{r, include=FALSE}
save.image(file='cache.RData')
```
