# Set up

Let's get started. First, we'll need to set the `.libPaths()` since we are using a Singularity container.

```{r}
.libPaths(c('/usr/local/lib/R/site-library', '/usr/local/lib/R/library'))
```

- We'll also set a seed at the start of the notebook so that we can reproduce our results if we decide to re-run this notebook at some future date.   
- We also set `future.globals.maxSize`, see this link for discussion about why we do that (basically we might be exceeding the allowed global variable size so we make them bigger) https://satijalab.org/seurat/archive/v3.0/future_vignette.html

```{r}
library(future)
set.seed(61)
options(future.globals.maxSize = 4000 * 1024^5)
plan("multiprocess", workers = 4)
```

- Then we load all the libraries we need:
```{r}

library(RColorBrewer)
library(Seurat)
library(patchwork)
library(ggplot2)
library(dplyr)
library(hdf5r)
library(stringr)
library(biomaRt)
library(viridis)
library(SeuratDisk)
library(SeuratData)
library(msigdbr)
library('pbmc3k.SeuratData')
library('cbmc.SeuratData')
library('ifnb.SeuratData')
data("pbmc3k")
data("cbmc")
data("ifnb")
```
